Eliminating prior-bias from sparse-projection tomographic reconstructions

### 2020-06-22 paper/tci.tex
removed SSIM of slice- potato

%--------potato reconstruction--------------------------------------------------
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.185\columnwidth]{../images/potato/testIm_green.png}}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm_new.png}}\hfill
\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
\caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts. The reconstructed volumes can be viewed in~\cite{supp_paper}.}
\label{fig:potato_3D_results_A}
%------------------------------------------------------------------------
\begin{table}[!h]
\caption{SSIM of 3D reconstructed potato volumes from various methods. Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects. In this dataset alone, the new changes are in a homogeneous background. Hence, the FDK performs the best when the RoI alone is considered. However, it fails when the entire volume is considered due to the prominent streaky artefacts.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior\\+ l1-ls\end{tabular}} \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.807      & 0.712                                                               & 0.852                                                            \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.918}        & 0.870      & 0.871                                                               & 0.880                                                                  \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.878       & \textcolor{red}{0.928}    & 0.922                                                            & 0.895                                                                  \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.744        & 0.874       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}red RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.945}        & 0.804       & 0.721                                                               & 0.858                                                            \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}green RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.920}        & 0.872       & 0.886                                                               & 0.901                                                                  \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}cyan RoI in\\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & 0.879        & \textcolor{red}{0.928}       & 0.926                                                               & 0.903                                                                  \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}full \\slice Fig.~\ref{fig:potato3D_test}\end{tabular}} & 1 (ideal)                     & 0.746        & \textcolor{red}{0.903}       & 0.866                                                               & 0.868                                                                  \\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}

>>>>

%--------potato reconstruction--------------------------------------------------
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.185\columnwidth]{../images/potato/testIm_green.png}}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/fdkIm.png}}\hfill
\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/potato/csIm_new.png}}\hfill
\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/plainPriorIm.png}}\hfill
\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/potato/weightedPriorIm.png}}
\caption{Slice-A from 3D reconstruction of the potato with $5\%$ projection views--(b) has strong streak artefacts with unclear shadow of the potato, (c) largely blurred, (d) no new information detected (prior dominates) and (e) new information detected while simultaneously reducing streak artefacts. The reconstructed volumes can be viewed in~\cite{supp_paper}.}
\label{fig:potato_3D_results_A}
\end{figure}
%------------------------------------------------------------------------
\begin{table}[!h]
\caption{SSIM of 3D reconstructed potato volumes from various methods. Each RoI spans 7 consecutive slices where the test is different from all of the previously scanned objects. In this dataset alone, the new changes are in a homogeneous background. Hence, the FDK performs the best when the RoI alone is considered. However, it fails when the entire volume is considered due to the prominent streaky artefacts.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior\\+ l1-ls\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Selective\\prior\\+ l1-ls\end{tabular}} \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}red RoI\\volume\end{tabular}}   & 1 (ideal)                     & \textcolor{red}{0.939}        & 0.807      & 0.712                                                               & 0.852                                                            \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}green RoI\\volume\end{tabular}} & 1 (ideal)                     & \textcolor{red}{0.918}        & 0.870      & 0.871                                                               & 0.880                                                                  \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}cyan  RoI\\volume\end{tabular}} & 1 (ideal)                     &  0.878       & \textcolor{red}{0.928}    & 0.922                                                            & 0.895                                                                  \\ \hline
\textbf{\begin{tabular}[c]{@{}c@{}}full \\ volume\end{tabular}} & 1 (ideal)                     & 0.744        & 0.874       & 0.856                                                               & \textcolor{red}{0.857}                                                                  \\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}
